Verifying Interactive WebSocket Applications in TypeScript

### 2020-01-23 PLACES_2020/main.tex
PLACES: shorten code listing whitespace

\begin{figure}[!h]
\begin{lstlisting}[language=JavaScript]
import { Coordinate as Point } from "./Types";
import { Labels } from "./Constants";

export type S13 = { Pos: (payload: Point) => S15 }
export type S15 = [Labels.Lose, Point, S16]
		| [Labels.Draw, Point, S17]
		| [Labels.Update, Point, S18]
\end{lstlisting}  
\captionof{lstlisting}{Example encodings from \textit{Noughts and Crosses} \texttt{Svr} EFSM.}
\label{lst:svr}
\end{figure}

@@

\begin{figure}[!h]
\begin{lstlisting}[language=JavaScript, tabsize=4]
render() {
	...
	{board.map((row, x) => (
		board.map((col, y) => {
			const SelectPoint = this.props.Pos('click', (event: UIEvent) => {
				event.preventDefault()
				return { x, y }
			}
			return <SelectPoint><td>.</td></SelectPoint>
		}
	)}
	...	
}
\end{lstlisting}  
\captionof{lstlisting}{Model transition for message sending in 
\textit{Noughts and Crosses} \texttt{P1} implementation.}
\label{lst:clientapp}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{lstlisting}[language=JavaScript]
export type S13 = { Pos: (payload: Point) => S15 }
export type S15 = [Labels.Lose, Point, S16]
		| [Labels.Draw, Point, S17]
		| [Labels.Update, Point, S18]
\end{lstlisting}  
\captionof{lstlisting}{Example encodings from \textit{Noughts and Crosses} \texttt{Svr} EFSM.}
\label{lst:svr}
\end{figure}

@@

\begin{figure}[!h]
\begin{lstlisting}[language=JavaScript, tabsize=4]
// Inside some render() function..
{board.map((row, x) => (
	row.map((col, y) => {
		const SelectPoint = this.props.Pos('click', (event: UIEvent) => {
			event.preventDefault()
			return { x: x, y: y }}
		return <SelectPoint><td>.</td></SelectPoint>
})}
\end{lstlisting}  
\captionof{lstlisting}{Model transition for message sending in 
\textit{Noughts and Crosses} \texttt{P1} implementation.}
\label{lst:clientapp}
\end{figure}
